---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package includes the following rank-based testing procedures 

- adpRankTest: Kong, Ye and Weng (2026)
- cmpRankTest: Kong, Villasante Tezanos, Harrar (2022, Symmetry)
- ovlRankTest: Kong and Harrar (2020, JNA)

and the following mean-based testing procedures 

- cmpTest(method = "gct"): Gregory, Carroll, Baladandayuthapani and Lahiri (2015, JASA)
- cmpTest(method = "mpt"): Zhang and Wang (2021, CSDA)
- adpTest: XU, Lin, Wei and Pan (2016, Biometrika)
- ovlTest: Chen and Qin (2010 AOS)

```{r setup}
library(HDRankTest)
## basic example code

set.seed(123)
p = 300
n1 = 60
n2 = 80
mu1 = mu2 = rep(0, p)
arma1 = arma2 = list(ar = c(.4, -.1), ma = c(0.2, 0.3)) # L=3

X1 <- rData(p=p, n1, mu1, arma=arma1) 
X2 <- rData(p=p, n1, mu1, arma=arma1) 

####################
# Rank-Based Tests #
####################
# Kong, Ye and Weng (2026)
adpRankTest(X1, X2, W = "CV")

# Kong, Villasante Tezanos and Harrar (2022, Symmetry)
cmpRankTest(X1, X2, W = 0) # mpt


cmpRankTest(X1, X2, W = 0, method = "gct") # gct

# Kong and Harrar (2020, JNA)
ovlRankTest(X1, X2)


####################
# Mean-Based Tests #
####################

# Gregory, Carroll, Baladandayuthapani and Lahiri (2015, JASA) 
cmpTest(X1, X2, W = 0, method = "gct")

# Zhang and Wang (2021, CSDA)
cmpTest(X1, X2, method = "mpt")


# XU, Lin, Wei and Pan (2016, Biometrika)
adpTest(X1, X2, W = 0)

# Chen and Qin (2010 AOS)
ovlTest(X1, X2)



```
